The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-10-08 paper.qmd
added acknowledgement section

# load Libraries
library(tidyverse)
library(Vizumap)
library(ggplot2)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)
library(colorspace)
library(rgeos)
```

@@

>>>>

# load Libraries
library(tidyverse)
library(Vizumap)
library(RColorBrewer)
library(scales)
library(sf)
library(ggrepel)
library(urbnmapr)
library(flextable)
library(colorspace)
library(rgeos)
```

@@

# Acknowledgements
This work is supported in part by a scholarship from the the Australian Energy Market Operator. 
The R packages were used for this work were: `tidyverse` [@tidyverse], `Vizumap` [@Vizumap], `RColorBrewer` [@RColorBrewer], `scales` [@scales], `sf` [@sf], `ggrepel` [@ggrepel], `urbnmapr` [@urbnmapr], `flextable` [@flextable], `colorspace` [@colorspace], and `rgeos` [@rgeos]. 
The GitHub repository for this paper can be found at https://github.com/harriet-mason/ARSA-UncertaintyLitReview which contains the files required to reproduce this article in full.
